QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-09-14 Response/Response.tex

\documentclass[12pt,draftclsnofoot,onecolumn]{IEEEtran}

\renewcommand{\baselinestretch}{1.2}
\textwidth 7.2in
\oddsidemargin -0.3in

\ifodd 1
\newcommand{\rev}[1]{{\color{blue}#1}} %revise of the text
\else
\newcommand{\rev}[1]{#1}
\fi

\usepackage{booktabs}

\usepackage{bbm}
\usepackage{amssymb}

%\usepackage{algorithm}
\usepackage{algpseudocode}

\usepackage{amssymb,amsmath,color,graphicx}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{times,graphicx, amsfonts}
\usepackage{multicol}
\usepackage{caption}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage{marvosym}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{setspace}
\usepackage{changepage}
\usepackage{float}
\usepackage{subcaption}
\usepackage{amsthm,amsbsy}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{mathtools}
\usepackage[sort,compress]{cite}
\usepackage[bookmarks=true]{hyperref}
\usepackage[ruled,commentsnumbered,linesnumbered]{algorithm2e}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\DeclareMathOperator*{\minimize}{minimize}

\newtheorem{theorem}{Theorem}
\newtheorem*{remark}{Remark}

\newenvironment{my}[2]%
{\begin{list}{}%
{\setlength{\rightmargin}{#1}\setlength{\leftmargin}{#2}}%

 \item[]{}

} {\end{list}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
	In the realm of mobile edge computing (MEC), efficient computation task offloading plays a pivotal role in ensuring a seamless quality of experience (QoE) for users. Maintaining a high QoE is paramount in today's interconnected world, where users demand reliable services. This challenge stands as one of the most primary key factors contributing to handling dynamic and uncertain mobile environment. In this study, we delve into computation offloading in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We formulate the computation task offloading problem as a Markov decision process (MDP) to maximize the long-term QoE of each user individually. We propose a distributed QoE-oriented computation offloading (QECO) algorithm based on deep reinforcement learning (DRL) that empowers mobile devices to make their offloading decisions without requiring knowledge of decisions made by other devices. Through numerical studies, we evaluate the performance of QECO. Simulation results validate that QECO efficiently exploits the computational resources of edge nodes. Consequently, it can complete 14\% more tasks and reduce task delay and energy consumption by 9\% and 6\%, respectively. These together contribute to a significant improvement of at least 37\% in average QoE compared to an existing algorithm.
\end{abstract}

\begin{IEEEkeywords}
	Mobile edge computing, computation task offloading, quality of experience, deep reinforcement learning.
\end{IEEEkeywords}

\section{Introduction}

Mobile edge computing (MEC) \cite{mao2017survey} has emerged as a promising technological solution to overcome the challenges faced by mobile devices (MDs) when performing high computational tasks, such as real-time data processing and artificial intelligence applications \cite{zhou2019edge} \cite{yousefpour2019all}. In spite of the MDs' technological advancements, their limited computing power and battery may lead to task drops, processing delays, and an overall poor user experience. By offloading intensive tasks to nearby edge nodes (ENs), MEC effectively empowers computation capability and reduces the delay and energy consumption. This improvement enhances the users' QoE, especially for time-sensitive computation tasks \cite{TNSE-QOE-24} \cite{ shah2018hierarchical}.

Efficient task offloading in MEC is a complex optimization challenge due to the dynamic nature of the network and the variety of MDs and servers involved \cite{jiang2019toward} \cite{TNSE-WU-24}. In particular, determining the optimal offloading strategy, scheduling the tasks, and selecting the most suitable EN for task offloading are the main challenges that demand careful consideration. Furthermore, the uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges that can significantly impact the computation offloading performance in MEC systems with limited resources.

\subsection{Related Work}
%Researchers have recently proposed several task offloading algorithms to tackle the aforementioned issues. Mao \textit{et al.} in \cite{mao2016dynamic} introduced a computation offloading algorithm for MEC systems. This scheme aims to reduce the MD's energy consumption while meeting the computation delay constraints. In \cite{zhang2016energy}, Zhang \textit{et al.} proposed an offloading scheme for MEC in heterogeneous cellular networks, taking into account the energy-constrained MEC scenario and the heterogeneity of MDs when optimizing the offloading decisions. Bi \textit{et al.} in \cite{bi2018computation} proposed an algorithm to optimize decision-making about computation offloading and power transferring in a wireless-powered MEC. Ning \textit{et al.} in \cite{ning2018cooperative} introduced a heuristic algorithm designed to enhance the efficiency of the partial computation offloading model. The works in \cite{mao2016dynamic}-\cite{ning2018cooperative} primarily focus on quasi-static systems and are not well-suited for dynamic systems and time-varying conditions.

%The uncertain requirements and sensitive latency properties of computation tasks in MEC systems with limited resources pose nontrivial challenges that can significantly impact the computation offloading performance. In \cite{jovsilo2019wireless}, Josilo \textit{et al.} proposed a distributed algorithm based on a Stackelberg game. Lee \textit{et al.} in \cite{lee2019online} designed an algorithm based on online optimization techniques to minimize the maximum delay of the tasks in a hybrid edge-cloud network. Yang \textit{et al.} in \cite{yang2018distributed} explored an overhead minimization problem, aiming to jointly optimize delay and energy consumption in MEC. They proposed a distributed offloading algorithm to mitigate the wireless channel competition among MDs. The works \cite{jovsilo2019wireless}-\cite{yang2018distributed} considered delay-tolerant tasks, which may have a limited applicability due to the real-time processing demand of high computational tasks. Compared to these works, we explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, which poses a more complex challenge.

%presents a more challenging problem. The impact of processing deadlines on the dynamic workload at the ENs influences the delay experienced by the offloaded tasks.

%In \cite{mao2016dynamic,zhang2016energy,bi2018computation,ning2018cooperative}, the processing capacity assigned to each MD by an EN remained unaffected by the number of offloaded tasks, resulting in a heavy load on the EN when a significant number of MDs offload their tasks to it. This heavy load can cause significant processing delays and even lead to missed deadlines and dropped tasks. To mitigate this issue, some existing works have proposed task offloading algorithms that consider the workloads at the ENs. In \cite{chen2018task}, Chen \textit{et al.} proposed an algorithm for task offloading in a software-defined ultra-dense network. The goal of this algorithm is to minimize task delay by formulating the task offloading scheme as a mixed integer non-linear program problem. Shah-Mansouri \textit{et al.} in \cite{shah2018hierarchical} proposed a QoE maximization slotwork for offloading decisions based on computation energy and delay reduction. They formulated a potential game to model competition among IoT users and achieved a close-to-optimal social cost.

To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, deep reinforcement learning (DRL) hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives \cite{arulkumaran2017deep}. DRL can effectively tackle the challenges of MEC arising from the ever-changing nature of networks, MDs, and servers' heterogeneity. This ultimately improves the MD users' QoE. In \cite{huang2019deep}, Huang \textit{et al.} focused on a wireless-powered MEC. They proposed a DRL-based  approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. In \cite{Bolourian-WCL24}, the authors proposed an offloading algorithm using deep Q-learning for wireless-powered Internet of Things (IoT) devices in MEC systems. This algorithm aims to minimize the task drop rate while the devices solely rely on harvested energy for operation. In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility. In this approach, each MD requires quality-of-service information from other MDs. Tang \textit{et al.} in \cite{9253665} investigated the task offloading problem for indivisible and deadline-constrained computational tasks in MEC systems. The authors proposed a distributed DRL-based offloading algorithm designed to handle uncertain workload dynamics at the ENs. Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources. 
%In \cite{chen2019energy}, Chen \textit{et al.} introduced an online algorithm with polynomial time complexity for offloading in MEC. This algorithm achieves a close-to-optimal energy consumption while ensuring that the delay is bounded. 
Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. In \cite{huang2021deadline}, Huang \textit{et al.} proposed a DRL-based method based on a partially observable MDP, which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. Liu  \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to study MEC and modeled the interactions of the environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks. Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial IoT systems to jointly optimize task offloading and resource allocation in order to achieve lower  energy consumption and decreased task delay. Liao \textit{et al.} in \cite{liao2023online} introduced a double reinforcement learning algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption.

%Liao \textit{et al.} in \cite{liao2023online} introduced a double reinforcement learning algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency to minimize both task computation delay and energy consumption. In \cite{huang2021deadline}, Huang \textit{et al.} proposed a DRL-based method based on a partially observable MDP, which guarantees the deadlines of real-time tasks while minimizing the total energy consumption of MDs. Liu  \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. In \cite{chen2019energy}, Chen \textit{et al.} introduced an online algorithm with polynomial time complexity for offloading in MEC. This algorithm achieves a close-to-optimal energy consumption while ensuring that the delay is bounded. In \cite{dai2020edge}, Dai \textit{et al.} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to study MEC and modeled the interactions between the policy-system environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial internet of things system to jointly optimize task offloading and resource allocation, which can enable the system to achieve lower total cost of energy consumption and task delay. In \cite{gao2022large}, Gao \textit{et al.} introduced an attention-based multi-agent algorithm designed for decentralized computation offloading. This algorithm effectively tackles the challenges of dynamic resource allocation in large-scale heterogeneous networks.

%\cite{wu2023noma}

\subsection{Motivation and Contributions}
Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
%First, prior research in \cite{yang2018distributed} - \cite{shah2018hierarchical} - \cite{9253665} considered delay-tolerant tasks, which may not be realistic due to the real-time processing demand by high computational tasks. Compared to these works, we explore a different and more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, which presents a more challenging problem. The impact of processing deadlines on the dynamic workload at the edge nodes influences the delay experienced by the offloaded tasks. 
QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay, as assumed in \cite{huang2019deep}--\cite{sun2024hierarchical}, but also by energy consumption. Albeit some existing works such as \cite{dai2020edge}--\cite{liao2023online}, have investigated the trade-off between delay and energy consumption, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.  In contrast to the aforementioned works \cite{huang2019deep}--\cite{liao2023online}, we propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their  demands. We also explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, posing a more intricate challenge.

%The works \cite{jovsilo2019wireless}-\cite{yang2018distributed} considered delay-tolerant tasks, which may have a limited applicability due to the real-time processing demand of high computational tasks. Compared to these works, we explore a more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, which poses a more complex challenge.

%Nevertheless, prior research in \cite{huang2019deep}-\cite{gao2022large} fails to tackle some or all of these challenges.

%Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. First, some existing works such as [] - [] considered delay-tolerant tasks, which may not be realistic due to the real-time processing demand by high computational tasks. Compared to the aforementioned works [10]–[15], we explore a different and more realistic MEC scenario involving delay-sensitive tasks with processing deadlines, which presents a challenging problem. The impact of processing deadlines on the dynamic workload at the edge nodes influences the delay experienced by the offloaded tasks. Second, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay as assumed in \cite{zhao2019deep}-\cite{9253665}, but also by energy consumption. Nevertheless, prior research in \cite{huang2019deep}-\cite{gao2022large} fails to tackle some or all of these challenges. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. In contrast to these works [18]–[21], we aim to propose a DRL-based distributed algorithm that provides users with an appropriate balance among QoE factors based on their demands, inferred from their state.

%Although DRL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. First, Some existing works such as [] - [] considered delay-tolerant tasks, which may not be realistic due to the real-time processing demand by high computational tasks. Comparing with the aforementioned works [10]–[15], we consider a different and more realistic MEC scenario.  We take into account delay-sensitive tasks with processing deadlines, which is chalenging to address because the processing deadlines will affect the load level dynamics at the edge nodes and hence affect the delay of the offloaded tasks. Secound, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay as assumed in  \cite{zhao2019deep}-\cite{9253665}, but also by energy consumption. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs. Nevertheless, prior research in \cite{huang2019deep}-\cite{gao2022large} fail to tackle some or all of these challenges. Different from those works [18]–[21], we aim to propose a DRL-based distributed algorithm that provide users with stricking balance among QoE factors based on their demands, caming from their state in each time.

In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We propose a distributed QoE-oriented computation offloading (QECO) algorithm that leverages DRL to efficiently handle task offloading in uncertain loads at ENs. This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.

%Inspired by existing studies, we delve into the challenge of computation task offloading in MEC systems, where the presence of strict task processing deadlines and energy constraints can adversely affect system performance and cause task delays. We proposes a decentralized offloading algorithm that empowers MDs to make intelligent decisions about offloading. The primary focus of our research is on the partial STO problem, where tasks can be fragmented into smaller sub-tasks, and the workloads at ENs can fluctuate dynamically and unpredictably. Our primary objective is to enhance the users' QoE individually. To define the problem, we have formulated the energy constraint MEC system as a Markov decision process (MDP) problem. To solve the MDP problems, Reinforcement Learning provides a range of solution methods such as dynamic programming, Monte Carlo methods, and temporal-difference learning. To deal with the Curse of Dimensions, modern Reinforcement Learning methods apply nonlinear function approximation, such as deep Q-network (DQN), to solve the problem with large state and action spaces. In our proposed approach, we leverage deep Q-learning \cite{mnih2015human}, a model-free DRL technique that enables agents to make informed decisions based on local observations without explicit knowledge of the system's dynamics and modeling. Compared to other researches, our approach provides a more realistic MEC scenario and a promising solution to the challenging problem of task offloading with strict deadline constraints. The proposed algorithm, by only utilizing locally observed information, allows each MD to determine the offloading decision in a decentralized manner.

Our main contributions are summarized as follows:

### 2024-09-17 Revision/Paper_Rev.tex
FixBUG

@@

%methods, advances, drawbacks \textcolor{black}
\begin{table*}[htbp]\textcolor{blue}{
	\renewcommand{\arraystretch}{0.7}
	\captionsetup{name=TABLE}
	\caption{Comparison of Related Works Characteristic}
	\scalebox{1}{%
		\begin{tabular}{ lp{1.7cm}p{3cm}p{3.4cm}p{0.8cm}p{2.2cm}p{3cm}l} 
			\toprule
			\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Algorithm/Methods} &  \textbf{Drawbacks}  \\ \midrule
			\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
			\cite{Bolourian-WCL24} - & MEC with EH devices& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & Deep Q-Learning & Not consider computation delay  \\\midrule
			\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
			\cite{9253665} = &  MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
			\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
			\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's deman into consideration \\\midrule
			\cite{huang2021deadline} = & MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
			\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & MADRL &  Not consider delay-sensitive tasks \\\midrule
			\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule
			\cite{gao2022large} - & heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
			\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's deman into consideration\\\midrule
			\cite{liao2023online} = & MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
			\cite{wu2023multi} - & MEC-based IIoT & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN& \\\midrule
			\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & MARL & \\\midrule
			\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent DDPG & \\\midrule
			\cite{wu2024combining} - & MEC-based IIoT & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & DDPG  & \\\midrule
			QECO &  MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
			\toprule
	\end{tabular}}
	\label{table1}}
\end{table*}

\newpage.

\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.7}
		\captionsetup{name=TABLE}
		\caption{Comparison of Related Works Characteristic}
		\scalebox{1}{%
			\begin{tabular}{ lp{1.7cm}p{3cm}p{3.4cm}p{0.8cm}p{2.2cm}p{3cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Algorithm/Methods} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} = & MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent DDPG & \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & MARL & \\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's deman into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & MADRL &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's deman into consideration\\\midrule
				\cite{gao2022large} - & heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent DDPG & Not take user's deman into consideration \\\midrule
				\cite{9253665} = &  MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining} - & MEC-based IIoT & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & DDPG  & \\\midrule
				\cite{wu2023multi} - & MEC-based IIoT & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN& \\\midrule
				\cite{huang2021deadline} = & MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24} - & MEC with EH devices& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & Deep Q-Learning & Not consider computation delay  \\\midrule
				QECO &  MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table1}}
\end{table*}
\newpage.
\newpage.
\newpage.
\newpage

\section{Related Work}

@@

\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, Internet of Vehicles (IoV) \cite{.}, and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}. Table~\ref{table1} provides an intuitive comparison of the related works.}

\subsection{DRL-Based Computation Offloading Optimization in MEC}
To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, deep reinforcement learning (DRL) hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives \cite{arulkumaran2017deep}. DRL can effectively tackle the challenges of MEC arising from the ever-changing nature of networks, MDs, and servers' heterogeneity. This ultimately improves the MD users' QoE.

Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to study MEC and modeled the interactions of the environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. Liao \textit{et al.} in \cite{liao2023online} introduced a double reinforcement learning algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. 
  In \cite{huang2019deep}, Huang \textit{et al.} focused on a wireless-powered MEC. They proposed a DRL-based  approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration.
 To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for IIoT network. They modeled the problem as an MDP and proposed a multi-agent DDQN-based algorithm.
  In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility. In this approach, each MD requires quality-of-service information from other MDs. 
  Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources. 
  Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC netwrok. They used an MDP and proposed a MARL method to minimize both energy consumption and processing delay.
  Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. Liu  \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL (MADRL), which can generate interactive information along with resource decisions. Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial IoT systems to jointly optimize task offloading and resource allocation in order to achieve lower  energy consumption and decreased task delay.

  In these researchs authours mostly investigated MEC networks and explored computation offloading proble, but in some works such as \cite{zhou2021deep} \cite{liao2023online} have mainly focused on single MEC network model, and has not taken into account the challenges of dynamic network environment with multiple ENs. In fact, the channel quality, requested task, and energy state on an MDs all change dynamically with time in an actual MEC scenario, thus a more realistic MEC scenario is needed, involving delay-sensitive tasks with processing deadlines in multiple MDs and ENs, which poses a more intricate challenge.

 \subsection{Queuing Theory for Computation Offloading}

>>>>

%\usepackage{hyperref}
%\hypersetup{
%	colorlinks = true,
%	citecolor = {blue}
%}

@@

\textcolor{blue}{To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives \cite{arulkumaran2017deep}. RL can effectively tackle the challenges of MEC arising from the ever-changing nature of networks, MDs, and servers' heterogeneity. This ultimately improves the MD users' QoE. We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. To minimize energy consumption, Munir \textit{et al.} \cite{munir2021multi} developed a semi-distributed approach using a multi-agent RL (MARL) framework for self-powered MEC. Gong \textit{et al.} in \cite{gong2022edge} proposed a DRL-based network structure in the industrial IoT (IIoT) systems to jointly optimize task offloading and resource allocation to achieve lower energy consumption and decreased task delay. To investigate privacy aware computation offloading problem, Wu \textit{et al.} in \cite{wu2024combining} proposed a deep Q-network (DQN)-based method. They transform the problem on MDP to optimize computation rate and energy consumption in a queuing-based IIoT network. Sun \textit{et al.} in \cite{sun2024hierarchical} explored both computation offloading and service caching problems in MEC. They formulated an optimization problem that aims to minimize the long-term average service delay. They then proposed a hierarchical DRL framework, which effectively handles both problems under heterogeneous resources.}

@@

\subsection{Related Work}
%\textcolor{black}{We explore state-of-the-art techniques characteristic to discuss how they address task offloading problems in scenarios that need to process massive data with limited devices in MEC, such as the Internet of Things (IoT), Internet of Vehicles (IoV), and Industrial IoT (IIoT)  environment.

%Internet of Things (IoT) \cite{dai2020edge}, \cite{liao2023online}, \cite{Bolourian-WCL24}, 
%Internet of Vehicles (IoV) \cite{Bolourian-WCL24}, 
%and Industrial IoT (IIoT)  environment \cite{gong2022edge}, \cite{wu2023multi}, \cite{wu2024combining}

%\subsubsection{DRL-Based Task Offloading Optimization in MEC}

\textcolor{blue}{
	In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment. To take advantage of RL methods for online computation offloading in MEC, Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC. They proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL (MADRL), which can generate interactive information along with resource decisions. Zhou \textit{et al.} in \cite{zhou2021deep} used an MDP to model the interactions of the environment. They proposed a Q-learning approach to achieve optimal resource allocation strategies and computation offloading. Liao \textit{et al.} in \cite{liao2023online} introduced a double DRL algorithm for performing online computation offloading in MEC. This algorithm optimizes transmission power and scheduling of CPU frequency when minimizing both task computation delay and energy consumption. }

\textcolor{blue}{
In these researches authors investigated simple MEC networks and explored computation offloading problems, mainly focused on delay-tolerant tasks or single MEC network model, and did not take into account the challenges of dynamic network environment with the variety of MDs and servers involved. In actual scenarios, an MEC system can provide delay-constrained services for serval MDs and ENs at the same time, while the works \cite{huang2019deep}, \cite{liu2021learn} not consider delay-sensitive tasks for network model and \cite{zhou2021deep}, \cite{liao2023online} just considered the situation of a single server or user in the MEC system.}

\textcolor{blue}{  
 In fact, the state of MD's computing and transmission power, arrived task's requirement, the energy state of MDs, and workloads at ENs all change dynamically with time in actual systems, thus a more realistic MEC scenario is needed. Besides the works \cite{huang2019deep}--\cite{liao2023online}, Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a MARL method to minimize both energy consumption and processing delay. Dai \textit{et al.} in \cite{dai2020edge} introduced the integration of action refinement into DRL and designed an algorithm to concurrently optimize resource allocation and computation offloading. To optimize privacy protection and quality of service, authors in \cite{wu2024privacy} investigated the joint computation offloading and power allocation problems for the IIoT network. They modeled the problem as an MDP and proposed a multi-agent DDQN-based algorithm.
In \cite{zhao2019deep}, Zhao \textit{et al.} proposed a computation offloading algorithm based on DRL, which addresses the competition for wireless channels to optimize long-term downlink utility. In this approach, each MD requires quality-of-service information from other MDs.}

  %In these researchs authours mostly investigated MEC networks and explored computation offloading problem, but in some works such as \cite{zhou2021deep} \cite{liao2023online} have mainly focused on single MEC network model, and has not taken into account the challenges of dynamic network environment with multiple ENs. In fact, the channel quality, requested task, and energy state on an MDs all change dynamically with time in an actual MEC scenario, thus a more realistic MEC scenario is needed, involving delay-sensitive tasks with processing deadlines in multiple MDs and ENs, which poses a more intricate challenge.
